\textbf{Erweiterte Sicherheits-Modellierung (3/3)} (\texttt{ConcreteDesignModel} in \texttt{Security.hs})\\

Mengen: $\tobespecified{TamperProtection}$ \\

\textbf{Tamper Protection}: \\
\underline{Intuition}: A tamper protection is some way to prevent entities from physically manipulating hardware.
For example seals, locks, lockable storage, or plain isolation. \\
\underline{Syntax}: Tamper Protection: The set of tamper protection labels used in stereotypes applications. Computed and fixed at the beginning of the analysis. % are modelled by a component with the stereotype $<<TamperingMethod>>$:\\
\underline{Semantics}: $TamperProtections := \{p \mid \exists \, stereotype~application <<x~tamper~protection~p>>\}$\\%\{c | hasStereotype(c, <<TamperingMethod>>)\}$.
% \discuss{Are there better ways to model this than with components? Datatypes or enums for example?}

\textbf{Securing Ressource Container} \\
\underline{Intuition}: A Ressource Container is secured against tampering with a set of anti tampering methods.\\
\underline{Syntax} A ressource container is secured against tampering by $tm$ with the stereotype $<<TamperProtection~tm>>$.\\
\underline{Semantics}: $containerTamperableByAttackerWithAbilities(c, abilities)$ iff $\exists \, t \in abilities \mid hasStereotype(c, <<TamperProtection~t>>)$. %$\{t \mid hasStereotype(c, <<TamperProtection~t>>)\} \subseteq abilities$.
% \discuss{Here the attacker has to have all tamper abilities. One is not sufficient. Do we want this?}

\textbf{Tampering Adversaries}\\
\underline{Intuition} An attacker can break one or several tamper protections.
This is part of the ability Specification of adversaries.\\
\underline{Syntax}: An adversary can break the tamper protection $t$, if it has the stereotype $<<CanTamper~t>>$.\\
\underline{Semantics}: $tamperingAbilites(a,t)$ iff $hasStereotype(a,<<CamTamper~t>>)$.


Relationen:
\begin{description}
  \item[$\tobespecified{tamperingAbilites(Attacker, TamperingMethods)}$]
        mit $\tobespecified{tamperingAbilites}(a, ta)$ gdw. Angreifer $a$ die
        Tampering-Methode $ta$ beherrscht.

  \item[$\tobespecified{containerTamperableByAttackerWithAbilities(ResourceContainer,
        \mathcal{P}\left(TamperingMethods\right))}$]
        mit $\tobespecified{containerTamperableByAttackerWithAbilities(c, abilities)}$ gdw. die Fähigkeiten $abilities$ ausreichen, den Container $c$ zu knacken
\end{description} 
